30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-10 paper.tex
two spaces
Added text about Gnutella and Freenet

\section{Current decentralized systems}
\section{Which components needs to be decentralized of Tor?}
\section{Comparison existing  networks}

>>>>

\section{Current decentralized systems}

\section{Which components needs to be decentralized of Tor?}

\section{Comparison existing decentralized  networks}
Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

\subsection{Gnutella}
Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called 'servents', a combination of servers and clients. Each client can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available. These peers can be found on http://gnutellahosts.com. Once the peer has joined, there are several messages a servant can send out:
\begin{itemize}
\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
\item To transfer items between peers, the GET and PUSH messages are being used.
\end{itemize}
Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file. To search for a file, a flooding algorithm is used.

\subsection{Freenet}
In Freenet, each data item is represented by a key that is independent of the location of the file. Freenet is called a loosely structured network because of this. To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.\\\\
There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file. Another key is the Signed-Subspace key which enables personal namespaces. This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file. The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.\\\\
The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded anymore. Results of queries are being cached in intermediate nodes to reduce the time for a query response.

\subsection{Freehaven}

\subsection{Tapestry}

\subsection{Kademlia}

\subsection{Tarzan}
